Legion: Expressing Locality and Independence with Logical Regions

### 2012-04-04 doc/sc2012/code_ex.tex
most of the copy code cleaned up - reductions not quite right

  CircuitPiece pieces[MAX_PIECES];
  for(i = 0; i #$<$# MAX_PIECES; i++) 
    pieces[i] = { rn_pvt = p_pvt_nodes[i], rn_shr = p_shr_nodes[i],
                  rn_ghost = p_ghost_nodes[i], rw_pvt = p_wires[i] };
  while(!done) {
    spawn (i = 0; i #$<$# MAX_PIECES; i++) calc_new_currents(pieces[i]);
    spawn (i = 0; i #$<$# MAX_PIECES; i++) distribute_charge(pieces[i]);
    spawn (i = 0; i #$<$# MAX_PIECES; i++) update_voltages(pieces[i]);
  }
}

>>>>

  CircuitPiece pieces[MAX_PIECES];
  for(i = 0; i #$<$# MAX_PIECES; i++) 
    pieces[i] = { rn_pvt: p_pvt_nodes[i], rn_shr: p_shr_nodes[i],
                  rn_ghost: p_ghost_nodes[i], rw_pvt: p_wires[i] };
  while(!done) {
    spawn (i = 0; i #$<$# MAX_PIECES; i++) calc_new_currents(pieces[i]);
    spawn (i = 0; i #$<$# MAX_PIECES; i++) distribute_charge(pieces[i]);
    spawn (i = 0; i #$<$# MAX_PIECES; i++) update_voltages(pieces[i]);
  }
}
